---
title: "Iso2k NSF EAR"
author: "Matthew J. Berens"
date: "11/19/2020"
output: html_document
---

```{r setup, include=FALSE}
options(scipen = 10, digits = 4) #Removes scientific notation
library(magrittr)
library(tidyverse)
library(lipdR)
load("iso2k1_0_0.RData")
```

## R Markdown
Script name: Iso2k analysis for MJB NSF-EAR Postdoc Application

Purpose of script: Filter records from full Iso2k database

Script author: M. Berens

Date updated: 2020-06-10


Citation: Konecky et al. (2020) The Iso2k Database: A global compilation of paleo-d18O and d2H records to aid understanding of Common Era climate

Database is available for download from https://doi.org/10.25921/57j8-vs18 or http://lipdverse.org/iso2k/current_version/


```{r sorting}
## extract all Iso2k UIDs
TSids <- as.character(sapply(sTS, "[[", "paleoData_iso2kUI"))

```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
